CS222 Project Proposal

### 2019-12-10 proposal/proposal.tex
embedding related work

\author{Yichen Xie}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{}          %% \email is recommended

\author{Zhongye Wang}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
\email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended

\author{Xinyu Zhan}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{}          %% \email is recommended

@@

% zxy
\section{Related Work}
\paragraph{\textbf{Ensemble method}} 
Ensemble method solves the learning problem by combining several learners.
A few researchers have addressed the issue of combining a set of simple classifier. 
Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
However, this method actually increased the amount of computation since it trained the learned repeatedly.
Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieves arbitrarily high accuracy by combining a set of weak learners.
This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
Subsequent weak learners are tweaked in favor of those instances misclassified by previous classifiers. 
Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.

@@

% Bibliography
% \bibliographystyle{acm}
\bibliographystyle{unsrt}
\bibliography{../full_list.bib}

>>>>

\author{Zhongye Wang}
\authornote{Student Number: 517030910353, Parallel Authorship}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended

\author{Yichen Xie}
\authornote{Student Number: 517030910355, Parallel Authorship}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{}          %% \email is recommended

\author{Xinyu Zhan}
\authornote{Student Number: 517030910358, Parallel Authorship}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{}          %% \email is recommended

@@

% zxy
\section{Related Work}
% embedding
As mentioned before, our approach resembles the embedding method, which is a common practice to address the curse of dimensionality, where we map data points into a subspace with reduced dimensionality and carry out the task in this space \cite{2016ml}.
This can be accomplished with Multiple Dimension Scaling (MDS) \cite{cox2000multidimensional} or implicitly train an embedding in the hidden layers of a neural network.
However, we explicitly search for an embedding by searching the optimal discriminator set, where each discriminator simulates one component in the embedding and we could directly obtain the category of some samples.
It is also possible to consider more complex way of classifying using the embedding like adding another layer of network to perform the classification step, but we will stick to the current setting in the early stages of the development.

@@

% Bibliography
% \bibliographystyle{acm}
% \bibliographystyle{unsrt}
\bibliography{../full_list.bib}
